Meta-analysis

### 2019-09-15 05_MetaAnalysis.Rmd
Use sampling variance only studies on line 499

# and replacing the values in the dataset
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
   Sv
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$y_error.type <-
   "SamplingVariance"

```

@@

PM_MB_means_T <- PM_MB_means %>%
   group_by(trial_ref) %>%
   summarise(
      trial_mean = mean(grain_yield.t.ha, na.rm = TRUE),
      BW_trial_variance = sd(grain_yield.t.ha, na.rm = TRUE) ^ 2
   )

@@

plot(BW_trial_variance ~ trial_mean, data = PM_MB_means)
abline(-0.01356, 0.03076)

```

>>>>

# and replacing the values in the dataset
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
   Sv
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$y_error.type <-
   "SamplingVariance"
```

@@

PM_MB_means_T <- PM_MB_means.SV %>%
   group_by(trial_ref) %>%
   summarise(
      trial_mean = mean(grain_yield.t.ha, na.rm = TRUE),
      BW_trial_variance = sd(grain_yield.t.ha, na.rm = TRUE) ^ 2
   )

@@

plot(BW_trial_variance ~ trial_mean, data = PM_MB_means)
abline(-0.01356, 0.03076)
```
